---
title: "Anaylsis of 911onFox Tweets"
description: |
  A new article created using the Distill format.
author:
  - name: Lissie Bates-Haus, Ph.D. 
    url: https://github.com/lbateshaus
    affiliation: U Mass Amherst DACSS MS Student
    affiliation_url: https://www.umass.edu/sbs/data-analytics-and-computational-social-science-program/ms
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

This document is a practice project for scraping data from Twitter. The topic for this project is the television show 911 on the Fox Network. The goal of this project is to create a wordcloud of hashtags in tweets the reference 911onFOX.

First, I will load in the previously-created csv file:

```{r}

#code was run in a different document and scrape saved to a csv.
#tweets2 <- search_tweets("911onFOX", n = 5000, token=mytoken) 
#write_as_csv(tweets2,"tweets2.csv")

library(readr)library(rtweet)
library(leaflet)
library(quanteda)
library(readr)
library(shiny)
library(rCharts)
library(lubridate)
library(highcharter)
library(leaflet)

#tweets2 <- read_csv("Text as Data/911Fox Project/tweets2.csv") #I used the import feature in RStudio
View(tweets2)

```

We now have a dataframe of 4823 observations over 90 variables.

A quick sort of the data shows us that the tweets were created from 2022-02-26 10:05:19 through 2022-03-04 15:54:02 (scrape was performed on 3/4/2022).

```{r}



```
 
